Modeling memory and taxis to analyze migrations

### 2021-01-13 code/StrategicVsTactical_PartI_v2.Rmd
minor changes to implement world

eval <- FALSE
if(eval){
  ResourceSim <- runManyYears(pop.Year1, Time, Resource = fixed.Resource, Parameters = parameters, n.years = 3)
  save(ResourceSim, file = "../results/ResourceSim.rda")
} else load("../results/ResourceSim.rda")

@@

eval <- FALSE
if(eval){
  MemResourceSim <- runManyYears(pop.Year1, Time, Resource = fixed.Resource, Parameters = parameters, n.years = 3)
  save(MemResourceSim, file = "../results/MemResourceSim.rda")
} else load("../results/MemResourceSim.rda")

>>>>

eval <- FALSE
if(eval){
  ResourceSim <- runManyYears(World, Parameters = parameters, n.years = 3)
  save(ResourceSim, file = "../results/ResourceSim.rda")
} else load("../results/ResourceSim.rda")

@@

eval <- FALSE
if(eval){
  MemResourceSim <- runManyYears(World, Parameters = parameters, n.years = 3)
  save(MemResourceSim, file = "../results/MemResourceSim.rda")
} else load("../results/MemResourceSim.rda")
